A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
Remove todo
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1080 43ef1190-90fd-4dd7-a769-d0121f02b80e
Ready to proofread and review
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1081 43ef1190-90fd-4dd7-a769-d0121f02b80e

\newcommand{\rdfterm}[1]{\texttt{#1}}
\newcommand{\pvalue}{\textit{p}-value\ }
\newcommand{\httph}[1]{\texttt{#1}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}

@@

We note that caching is not only useful for long-living information
resources, even though that may be the most important use. If a resource
is frequently requested, it may make sense to cache it even though it
may be fresh for only a very short period.

@@

RFC7234 defines two important headers: \httph{Expires}, whose value is
a date and time of when the response is considered stale, and
therefore should not be used; and \httph{Cache-Control}, which allows
detailed control of the cache, including a \httph{max-age} field,
which gives the time in seconds for how long the the response may be
used from the time of the request. \httph{max-age} takes precedence
over \httph{Expires}. In the following \emph{freshness lifetime} is
understood as the number of seconds that the response may be used
without contacting the origin server. Ideally, the calculation of the
freshness lifetime should be based of the above, we therefore shall
refer to this as ``standards-compliant caching''. However it can also
be based on heuristics, and Section~4.2.2 in RFC7234 provides some loose
constraints for such practice, as well as a suggestion for a useful
heuristic. This heuristic is based on a fraction of the time lapsed
between the current time and the modification time given in the
\httph{Last-Modified} header. This approach therefore still requires
the Web server to be cooperative to be successful. Commonly, Web
servers can track this, for example if RDF is served from a file
system the file modification time is used.

RFC7232, on the other hand, defines a protocol for asking the server
if the cached response is still fresh using conditional requests. This
doesn't burden the content provider with the task of estimating the
time to live beforehand, but then, it must be able to answer if the
resource has changed less expensively than serving the entire
response. Either of two headers must be set by the server to achieve
this: \httph{ETag}, which sets an opaque identifier for the response,
or \httph{Last-Modified} which gives the time and date of the last
modification of the resource. Clients may use these values to retrieve
the updated response only if the resource has changed. Other relevant
headers are described in Table~\ref{tab:headers}.
\todo{More on HTTP}

\begin{table}[tb]
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{1.4cm} | p{6.8cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogate-Capability} & Edge \cite{edgearch} & Draft
to allow fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww  & Header inserted by User
Agent to give details about problems with the download \\ \hline

>>>>

\newcommand{\rdfterm}[1]{\texttt{#1}}
\newcommand{\pvalue}{\textit{p}-value\ }
\newcommand{\httph}[1]{\texttt{#1}}
%\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}

@@

We note that caching is not only useful for long-living 
resources, even though that may be the most important use. If a resource
is frequently requested, it may make sense to cache it even though it
may be fresh for only a very short period.

@@

RFC7234 defines two important headers: \httph{Expires}, whose value is
a date and time of when the response is considered stale, and
therefore should not be used; and \httph{Cache-Control}, which allows
detailed control of the cache, including a \httph{max-age} field,
which gives the time in seconds for how long the the response may be
used from the time of the request. \httph{max-age} takes precedence
over \httph{Expires}. In the following \emph{freshness lifetime} is
understood as the number of seconds that the response may be used
without contacting the origin server. Ideally, the calculation of the
freshness lifetime should be based of the above, we therefore shall
refer to this as ``standards-compliant caching''. It can also
be based on heuristics, and Section~4.2.2 in RFC7234 provides some loose
constraints for such practice, as well as a suggestion for a useful
heuristic. This heuristic is based on a fraction of the time lapsed
between the current time and the modification time given in the
\httph{Last-Modified} header. This approach therefore still requires
the Web server to be cooperative to be successful. Commonly, Web
servers can track this, for example if RDF is served from a file
system the file modification time is used.

RFC7232, on the other hand, defines a protocol for asking the server
if the cached response is still fresh using conditional requests. This
doesn't burden the content provider with the task of estimating the
time to live beforehand, but then, it must be able to answer if the
resource has changed less expensively than serving the entire
response. Either of two headers must be set by the server to achieve
this: \httph{ETag}, which sets an opaque identifier for the response,
or \httph{Last-Modified} which gives the time and date of the last
modification of the resource. Clients that have obtained these values
may use them to validate an earlier response by using
\httph{If-None-Match} and/or \httph{If-Modified-Since} respectively in
a subsequent request. If the server finds the response has not changed
based on this, it will respond with a \httph{304} status code and no
body, otherwise it will return the full response. The other headers we
recorded are listed in Table~\ref{tab:headers}.

\begin{table}[bt]
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{1.4cm} | p{6.8cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogate-Capability} & Edge \cite{edgearch} & Draft
to allow fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww  & Header inserted by User
Agent to give details about problems with the download \\ \hline
